---
title: "Exercises"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.width = 7, fig.height = 5, out.height = "500px", fig.align = "center")
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_minimal(base_size = 16))
options(ggplot2.discrete.colour = RColorBrewer::brewer.pal(5, "Dark2"))
library(ggeffects)
options(show.signif.stars = FALSE)
library(lme4)
library(broom.mixed)
```

# Read data

```{r read-data}
sanker2020 <- read_csv("02-ident-discr/sanker2020.csv") %>%
  mutate(OrigCoda = factor(OrigCoda, levels = c("voiceless", "voiced")))


# Read SPP 2022 students' data
spp2022 <- read_delim("02-ident-discr/anonymous-session1.txt")

spp2022_ident <- spp2022 %>% filter(task == "identification") %>%
  mutate(
    step = as.numeric(str_sub(stimulus, 5, 5)),
    response = factor(response, levels = c("i", "_"))
  ) %>%
  select(participant:reactionTime, step)

spp2022_discr <- spp2022 %>% filter(task == "discrimination") %>%
  mutate(
    pair = case_when(
      stepA == stepB ~ 0,
      stepA == "step1" & stepB == "step3" ~ 2,
      stepA == "step3" & stepB == "step1" ~ 2,
      stepA == "step3" & stepB == "step5" ~ 4,
      stepA == "step5" & stepB == "step3" ~ 4,
      stepA == "step5" & stepB == "step7" ~ 6,
      stepA == "step7" & stepB == "step7" ~ 6
    ),
    correct = factor(wasResponsecorrect)
  ) %>%
  filter(pair > 0)
```

# Exercise 1: Identification task

Use the `spp2022_ident` data and run a linear model for identification data.

Check the tibble:

```{r spp22-ident}
spp2022_ident
```

Now model `response` as a function of `step`.

```{r spp22-ident-lm}
# Insert the right code in place of `...`
spp2022_ident_lm <- glmer(
  ...,
  data = ...,
  family = ...
)
```

Inspect the summary of the model.

```{r spp22-ident-lm-sum}
# Which function should you use to get the summary of the model?

...
```

And finally, plot the model results!

```{r spp22-ident-lm-plot}
...
```

# Exercise 2: Discrimination task

Try to run a model on the discrimination data as we just saw in class, but add ISI as another predictor in the model.

You will have to include an interaction between `pair` and `interstimulusInterval`, like so: `pair * interstimulusInterval`.

```{r spp22-discr-lm}
...
```

Does it work?
